Transport map accelerated adaptive importance sampling, and application to inverse problems arising from multiscale stochastic reaction networks

### 2018-06-12 TPAIS_2018.tex
Standardised bibliography

A range of numerical methods have been suggested to tackle this second
problem, including tau-leaping\cite{rathinam2003stiffness,cao2006efficient}, diffusion approximations\cite{erban2006gene,cotter2011constrained,cotter2016error}, quasi-steady state
approximations\cite{ea2005nested,cao2005slow}, and other averaging
arguments\cite{cotter2016constrained}. Some of these approaches are more
computationally intensive than others, but this can be mitigated with the
use of analytical results about the invariant densities of certain
types of fast subsystems\cite{jahnke2007solving,anderson2010product,anderson2016product}.

@@

The master equation for this model is only solvable in certain
situations, for example monomolecular networks\cite{jahnke2007solving}, or for
steady-state solutions certain deficiency
zero networks\cite{anderson2010product,anderson2016product}. Trajectories for this system can be
sampled exactly, for instance using the Gillespie SSA\cite{gillespie1977exact}, or
its variants\cite{gillespie2007stochastic,gibson1998efficient,cao2004efficient,anderson2007modified}. However, if the system is stiff, i.e. there
are some reactions which are firing many times on a timescale for
which others are unlikely to fire at all, then trajectories can become
prohibitively expensive to simulate, since these methods simulate
every single reaction event with the same cost. In such a system, one
might employ multiscale methods in order to approximate trajectories
at a lower cost than the exact algorithms.

>>>>

A range of numerical methods have been suggested to tackle this second
problem, including tau-leaping\cite{rathinam2003stiffness,cao2006efficient}, diffusion approximations\cite{erban2006gene,cotter2011constrained,cotter2016error}, quasi-steady state
approximations\cite{weinan2007nested,cao2005slow}, and other averaging
arguments\cite{cotter2016constrained}. Some of these approaches are more
computationally intensive than others, but this can be mitigated with the
use of analytical results about the invariant densities of certain
types of fast subsystems\cite{jahnke2007solving,anderson2010product,anderson2016product}.

@@

The master equation for this model is only solvable in certain
situations, for example monomolecular networks\cite{jahnke2007solving}, or for
steady-state solutions certain deficiency
zero networks\cite{anderson2010product,anderson2016product}. Trajectories for this system can be
sampled exactly, for instance using the Gillespie SSA\cite{gillespie1977exact}, or
its variants\cite{gillespie2007stochastic,cao2004efficient,anderson2007modified}. However, if the system is stiff, i.e. there
are some reactions which are firing many times on a timescale for
which others are unlikely to fire at all, then trajectories can become
prohibitively expensive to simulate, since these methods simulate
every single reaction event with the same cost. In such a system, one
might employ multiscale methods in order to approximate trajectories
at a lower cost than the exact algorithms.
